---
output: pdf_document
---
<!-- This is the title page. -->
\pagenumbering{gobble} <!-- Remove the page number on the title page. -->

\begin{centering}
 
\vspace*{1.5cm}

\LARGE University of St.Gallen

\vspace{0.5cm}

\Large School of Management, Economics, Law, Social Sciences, International Affairs and Computer Science

\vspace{3cm}

\LARGE {\bf A Detailed Analysis of `r playerName`’s Results}

\vspace{3cm}

\LARGE Noah Baiguini, Dorian Böhler

\vspace{0.5cm}

\Large (21-619-507), (15-613-433)

\vspace{1.5cm}

\Large \today

\vspace{0.5cm}

\Large Skills: Programming

\vspace{0.5cm}

\Large PhD Mario Silic

\end{centering}

\newpage

\pagenumbering{arabic}

# Introduction

```{r, echo = FALSE, results = 'asis'}
# Objects from report.R:
# - highestRank
# - numberOfMatches
# - overview
# - playerName

cat('This report is about **', playerName, '**, who is a tennis player', sep = '')

if(!is.na(overview$country)) { # In these if-statements, we check whether the respective information is missing.
  cat(' from ')
  
  if(overview$country == 'USA') {
    cat('the ')
  }
  
  cat(countrycode(overview$country, origin = 'ioc', destination = 'country.name')) # Change the IOC to the English country name.
}

cat('. ')

if(!is.na(overview$turnedPro) & !is.na(overview$active)) {
  cat('He turned pro in', overview$turnedPro, 'and is ')
  
  if(overview$active == 1) {
    cat('still active')
  } else {
    cat('not active any more')
  }
  
  cat('. ')
}

if(!is.na(overview$birthday)) {
  cat('He was born on ', format(overview$birthday, '%d %B %Y'), ', so he is now ', floor(time_length(Sys.Date() - overview$birthday, 'years')), ' years old.\n', sep = '')
} else {
  cat('\n')
}

if(!is.na(overview$lefty) & !is.na(overview$oneHandedBackhand)) {
  cat('\n', playerName, ' is a ', sep = '')
  
  if(overview$lefty == 1) {
    cat('lefty')
  } else {
    cat('righty')
  }
  
  cat(' and has a ')
  
  if(overview$oneHandedBackhand == 1) {
    cat('one-handed')
  } else {
    cat('two-handed')
  } 
  
  cat(' backhand.\n')
}

cat('\nHe ')

if(overview$active == 0) { # If not active any more, use past simple.
  cat('played', numberOfMatches, 'matches in total.')
} else if(overview$active == 1) { # If still active, use present perfect.
  cat('has played', numberOfMatches, 'matches so far.')
} # Importantly, active is never missing in the list of players.

if(!is.na(highestRank)) {
  cat(' The highest ranking achieved is ', highestRank, '.', sep = '')
}
```

\vspace{1cm}

# Winning percentages
Here are a few interesting match winning percentages:

```{r, echo = FALSE, results = 'asis'}
# Objects from report.R:
# - winningPercentage
# - winningPercentageOutdoor
# - winningPercentageIndoor
# - winningPercentageHard
# - winningPercentageClay
# - winningPercentageGrass
# - winningPercentageBestOfThree
# - winningPercentageBestOfFive
# - winningPercentageOneHandedBackhand
# - winningPercentageTwoHandedBackhand
# - winningPercentageTop10

options(knitr.kable.NA = 'Never played') # Display missing values as 'Never played'.

kable(data.frame(c('Total', 'Outdoor', 'Indoor', 'Hard court', 'Clay court',
                   'Grass court', 'Best of three', 'Best of five', 'Against players with a one-handed backhand', 'Against players with a two-handed backhand',
                   'Against top 10 players'),
                 c(winningPercentage, winningPercentageOutdoor, winningPercentageIndoor, winningPercentageHard, winningPercentageClay, 
                   winningPercentageGrass, winningPercentageBestOfThree, winningPercentageBestOfFive, winningPercentageOneHandedBackhand, winningPercentageTwoHandedBackhand,
                   winningPercentageTop10)), col.names = c('Category', 'Winning Percentage'))
```

The following figure shows the number of first, second, third, fourth, and fifth sets played and won including the winning percentages:

&nbsp;

```{r, echo = FALSE, fig.height = 3.5}
# Objects from report.R:
# - plotWinningPercentageSets

plotWinningPercentageSets
```

\newpage

In the following figure, you can see the winning percentages (matches, sets, and games) over time:

&nbsp;

```{r, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 3.5}
# WARNING = FALSE: If the player played only a few matches, geom_smooth() does not work properly and throws up many warnings. We do not want to see them in the report.

# Objects from report.R:
# - plotRatio4

plotRatio4
```

\vspace{1cm}

# Tournaments
The match winning percentages at the Grand Slams are as follows:

```{r, echo = FALSE, results = 'asis'}
# Objects from report.R:
# - winningPercentageGrandSlams

kable(winningPercentageGrandSlams, col.names = c('Tournament', 'Match Winning Percentage')) # Missing values are still displayed as 'Never played'.
```

```{r, echo = FALSE, results = 'asis'}
# Objects from report.R:
# - numberOfFinals
# - overview
# - playerName

if(numberOfFinals > 0) { # Check whether the player has reached at least one final.
  cat('In the figure on the next page, you can see the cumulative number of tournament wins. Black crosses indicate finals that', playerName, 'lost.\n')
  
  cat('\n&nbsp;')
} else {
  if(overview$active == 0) { # If not active any more, use past simple.
    cat(playerName, 'did never reach a final.')
  } else if(overview$active == 1) { # If still active, use present perfect.
    cat(playerName, 'has not reached any final yet.')
  }
}
```

```{r, echo = FALSE, message = FALSE, warning = FALSE, fig.height = 3.5}
# WARNING = FALSE: There is a warning if the player played only one final. We do not want to see this warning in the report.

# Objects from report.R:
# - numberOfFinals
# - plotFinals

if(numberOfFinals > 0) {
  plotFinals
}
```

\vspace{1cm}

```{r, echo = FALSE, results = 'asis'}
# Objects from report.R:
# - playerName
# - priceMoneyUSDollarTotal
# - results

if(mean(!is.na(results$priceMoneyUSDollar)) > 1/2) { # Include this section only if the price money of the player is not missing too often.
  cat('# Price Money\n')
  
  cat(playerName, '\'s total price money is ', priceMoneyUSDollarTotal, '. The following figure shows how it developed over time.\n', sep = '')
  
  cat('\n&nbsp;')
}
```

```{r, echo = FALSE, fig.height = 3.5}
# Objects from report.R:
# - plotPriceMoneyUSDollarTotalYearly
# - results

if(mean(!is.na(results$priceMoneyUSDollar)) > 1/2) {
  plotPriceMoneyUSDollarTotalYearly
}
```

```{r, echo = FALSE, results = 'asis'}
# Objects from report.R:
# - overview
# - results

if(mean(!is.na(results$priceMoneyUSDollar)) > 1/2) {
  cat('&nbsp;\n')
  
  if(overview$active == 1) { # If still active, say this.
    cat('It should be noted that', year(Sys.Date()), 'is not over yet.\n')
  }
}
```



```{r, echo = FALSE, results = 'asis'}
# Objects from report.R:
# - playerName
# - rSquared
# - runRegression

if(runRegression) { # We compute the linear probability model only if there are enough observations without missing values (otherwise the results do not make much sense).
  if(!is.nan(rSquared)) { # Additional reasonableness check.
    cat('\n# What affects the winning probability of ', playerName, '?\n', sep = '')
    
    cat('\nWe have estimated the effect of some variables on the winning probability, using a linear probability model. The following table shows the results:\n')
  }
}
```

```{r, echo = FALSE, results = 'asis'}
# Objects from report.R:
# - lpm
# - rSquared
# - runRegression

if(runRegression) {
  if(!is.nan(rSquared)) {
    kable(lpm %>% mutate(p.value = pvalue(p.value)) %>% filter(!is.na(estimate)), col.names = c('Predictor', 'B', 'SE', 't', 'p'), digits = c(0, 2, 3, 3, 3))
  }
}
```

```{r, echo = FALSE, results = 'asis'}
# Objects from report.R:
# - enoughSurfaces
# - lpm
# - overview
# - playerName
# - results
# - rSquared
# - runRegression

if(runRegression) {
  if(!is.nan(rSquared)) {
    if(enoughSurfaces) { # Provide the base group of surface only if surface is included in the regression.
      cat('\nThe base group is', levels(results$surface)[1], 'for the surface.\n')
    }
    
    cat('\nHere are a few interesting observations:\n')
    
    cat('\n')
    
    # In the lines 311-585, the if-statements check for every variable whether the estimated coefficient is statistically (p-value < 0.1) and economically (estimated coefficient > 0.005) significant.
    # Based on this, we make some possibly interesting statements. The only exception is surface, which we do not check for significance but simply compare the estimated coefficients.
    
    if(overview$active == 0) { # If not active any more, use past simple.
      if('Tournament at Home' %in% lpm$term) { # If 'Tournament at Home' is included in the regression, do this.
        if(isTRUE(lpm$p.value[lpm$term == 'Tournament at Home'] > 0.1 |
                  round(lpm$estimate[lpm$term == 'Tournament at Home'], digits = 2) == 0)) { # Not significant.
          cat('* It did not influence the winning probability whether', playerName, 'played at home or not.\n')
        } else if(!is.na(lpm$estimate[lpm$term == 'Tournament at Home'])) { # Significant.
          cat('*', playerName, 'played ')
          
          if(lpm$estimate[lpm$term == 'Tournament at Home'] > 0) {
            cat('better ')
          } else {
            cat('worse ')
          }
          
          cat('at home.\n')
        }
      }

      if(isTRUE(lpm$p.value[lpm$term == 'Outdoor'] < 0.1 & round(lpm$estimate[lpm$term == 'Outdoor'], digits = 2) != 0)) { # Significant.
        cat('*', playerName, 'played better ')
        
        if(lpm$estimate[lpm$term == 'Outdoor'] > 0) {
          cat('outdoor.\n')
        } else {
          cat('indoor.\n')
        }
      }
      
      if(all(c('Surface: Clay', 'Surface: Grass') %in% lpm$term)) { # Check whether the player played on hard, clay, and grass.
        if(!is.na(lpm$estimate[lpm$term == 'Surface: Clay']) & !is.na(lpm$estimate[lpm$term == 'Surface: Grass'])) {
          cat('* It seems that the order of preference for the surface was: ')
          
          if(lpm$estimate[lpm$term == 'Surface: Clay'] < 0 &
             lpm$estimate[lpm$term == 'Surface: Grass'] < lpm$estimate[lpm$term == 'Surface: Clay']) {
            cat('Hard, Clay, and Grass (ignoring Carpet).\n')
          } else if(lpm$estimate[lpm$term == 'Surface: Grass'] < 0 &
                    lpm$estimate[lpm$term == 'Surface: Clay'] < lpm$estimate[lpm$term == 'Surface: Grass']) {
            cat('Hard, Grass, and Clay (ignoring Carpet).\n')
          } else if(lpm$estimate[lpm$term == 'Surface: Grass'] > 0 &
                    lpm$estimate[lpm$term == 'Surface: Clay'] < 0) {
            cat('Grass, Hard, and Clay (ignoring Carpet).\n')
          } else if(lpm$estimate[lpm$term == 'Surface: Clay'] > 0 &
                    lpm$estimate[lpm$term == 'Surface: Grass'] < 0) {
            cat('Clay, Hard, and Grass (ignoring Carpet).\n')
          } else if(lpm$estimate[lpm$term == 'Surface: Clay'] > 0 &
                    lpm$estimate[lpm$term == 'Surface: Grass'] > lpm$estimate[lpm$term == 'Surface: Clay']) {
            cat('Grass, Clay, and Hard (ignoring Carpet).\n')
          } else if(lpm$estimate[lpm$term == 'Surface: Grass'] > 0 &
                    lpm$estimate[lpm$term == 'Surface: Clay'] > lpm$estimate[lpm$term == 'Surface: Grass']) {
            cat('Clay, Grass, and Hard (ignoring Carpet).\n')
          }
        }
      }
      
      if(isTRUE(lpm$p.value[lpm$term == 'Total Price Money (m$)'] < 0.1 & round(lpm$estimate[lpm$term == 'Total Price Money (m$)'], digits = 2) != 0)) { # Significant.
        cat('*', playerName, 'played ')
        
        if(lpm$estimate[lpm$term == 'Total Price Money (m$)'] > 0) {
          cat('better ')
        } else {
          cat('worse ')
        }
        
        cat('when there was more money to win.\n')
      }
      
      if(isTRUE(lpm$p.value[lpm$term == 'Opponent: Rank'] > 0.1 | round(lpm$estimate[lpm$term == 'Opponent: Rank'], digits = 2) == 0)) { # Not significant.
        cat('* The rank of the opponent did not substantially affect the winning probability.\n')
      } else if(!is.na(lpm$estimate[lpm$term == 'Opponent: Rank'])){ # Significant.
        if(lpm$estimate[lpm$term == 'Opponent: Rank'] > 0) {
          cat('* The winning probability increased ')
        } else {
          cat('* Surprisingly, the winning probability decreased ')
        }
        
        cat('with the rank of the opponent.\n')
      }
      
      if(isTRUE(lpm$p.value[lpm$term == 'Opponent: Age'] < 0.1 & round(lpm$estimate[lpm$term == 'Opponent: Age'], digits = 2) != 0)) { # Significant.
        cat('* The winning probability ')
        
        if(lpm$estimate[lpm$term == 'Opponent: Age'] > 0) {
          cat('increased ')
        } else {
          cat('decreased ')
        }
        
        cat('with the age of the opponent.\n')
      }
      
      if(isTRUE(lpm$p.value[lpm$term == 'Opponent: Height'] < 0.1 & round(lpm$estimate[lpm$term == 'Opponent: Height'], digits = 2) != 0)) { # Significant.
        cat('* The winning probability ')
        
        if(lpm$estimate[lpm$term == 'Opponent: Height'] > 0) {
          cat('increased ')
        } else {
          cat('decreased ')
        }
        
        cat('with the height of the opponent.\n')
      }
      
      if(isTRUE(lpm$p.value[lpm$term == 'Opponent: Lefty'] < 0.1 & round(lpm$estimate[lpm$term == 'Opponent: Lefty'], digits = 2) != 0)) { # Significant.
        cat('* The winning probability was ')
        
        if(lpm$estimate[lpm$term == 'Opponent: Lefty'] > 0) {
          cat('larger ')
        } else {
          cat('smaller ')
        }
        
        cat('against lefties.\n')
      }
      
      if(isTRUE(lpm$p.value[lpm$term == 'Opponent: One Handed Backhand'] < 0.1 & round(lpm$estimate[lpm$term == 'Opponent: One Handed Backhand'], digits = 2) != 0)) { # Significant.
        cat('* The winning probability was larger against players with a ')
        
        if(lpm$estimate[lpm$term == 'Opponent: One Handed Backhand'] > 0) {
          cat('one-handed ')
        } else {
          cat('two-handed ')
        } 
        
        cat('backhand.\n')
      }
      
      if(isTRUE(lpm$p.value[lpm$term == 'Best of Five'] < 0.1 & round(lpm$estimate[lpm$term == 'Best of Five'], digits = 2) != 0)) { # Significant.
        cat('* The winning probability was larger in ')
        
        if(lpm$estimate[lpm$term == 'Best of Five'] > 0) {
          cat('best-of-five ')
        } else {
          cat('best-of-three ')
        }
        
        cat('matches.\n')
      }
    } else if(overview$active == 1) { # If still active, use present perfect.
      if('Tournament at Home' %in% lpm$term) { # If 'Tournament at Home' is included in the regression, do this.
        if(isTRUE(lpm$p.value[lpm$term == 'Tournament at Home'] > 0.1 |
                  round(lpm$estimate[lpm$term == 'Tournament at Home'], digits = 2) == 0)) { # Not significant.
          cat('* It does not influence the winning probability whether', playerName, 'plays at home or not.\n')
        } else if(!is.na(lpm$estimate[lpm$term == 'Tournament at Home'])){ # Significant.
          cat('*', playerName, 'plays ')
          
          if(lpm$estimate[lpm$term == 'Tournament at Home'] > 0) {
            cat('better ')
          } else {
            cat('worse ')
          }
          
          cat('at home.\n')
        }
      }
      
      if(isTRUE(lpm$p.value[lpm$term == 'Outdoor'] < 0.1 & round(lpm$estimate[lpm$term == 'Outdoor'], digits = 2) != 0)) { # Significant.
        cat('*', playerName, 'plays better ')
        
        if(lpm$estimate[lpm$term == 'Outdoor'] > 0) {
          cat('outdoor.\n')
        } else {
          cat('indoor.\n')
        }
      }
      
      if(all(c('Surface: Clay', 'Surface: Grass') %in% lpm$term)) { # Check whether the player has played on hard, clay, and grass.
        if(!is.na(lpm$estimate[lpm$term == 'Surface: Clay']) & !is.na(lpm$estimate[lpm$term == 'Surface: Grass'])) {
          cat('* It seems that the order of preference for the surface is: ')
          
          if(lpm$estimate[lpm$term == 'Surface: Clay'] < 0 &
             lpm$estimate[lpm$term == 'Surface: Grass'] < lpm$estimate[lpm$term == 'Surface: Clay']) {
            cat('Hard, Clay, and Grass (ignoring Carpet).\n')
          } else if(lpm$estimate[lpm$term == 'Surface: Grass'] < 0 &
                    lpm$estimate[lpm$term == 'Surface: Clay'] < lpm$estimate[lpm$term == 'Surface: Grass']) {
            cat('Hard, Grass, and Clay (ignoring Carpet).\n')
          } else if(lpm$estimate[lpm$term == 'Surface: Grass'] > 0 &
                    lpm$estimate[lpm$term == 'Surface: Clay'] < 0) {
            cat('Grass, Hard, and Clay (ignoring Carpet).\n')
          } else if(lpm$estimate[lpm$term == 'Surface: Clay'] > 0 &
                    lpm$estimate[lpm$term == 'Surface: Grass'] < 0) {
            cat('Clay, Hard, and Grass (ignoring Carpet).\n')
          } else if(lpm$estimate[lpm$term == 'Surface: Clay'] > 0 &
                    lpm$estimate[lpm$term == 'Surface: Grass'] > lpm$estimate[lpm$term == 'Surface: Clay']) {
            cat('Grass, Clay, and Hard (ignoring Carpet).\n')
          } else if(lpm$estimate[lpm$term == 'Surface: Grass'] > 0 &
                    lpm$estimate[lpm$term == 'Surface: Clay'] > lpm$estimate[lpm$term == 'Surface: Grass']) {
            cat('Clay, Grass, and Hard (ignoring Carpet).\n')
          }
        }
      }
      
      if(isTRUE(lpm$p.value[lpm$term == 'Total Price Money (m$)'] < 0.1 & round(lpm$estimate[lpm$term == 'Total Price Money (m$)'], digits = 2) != 0)) { # Significant.
        cat('*', playerName, 'plays ')
        
        if(lpm$estimate[lpm$term == 'Total Price Money (m$)'] > 0) {
          cat('better ')
        } else {
          cat('worse ')
        }
        
        cat('when there is more money to win.\n')
      }
      
      if(isTRUE(lpm$p.value[lpm$term == 'Opponent: Rank'] > 0.1 | round(lpm$estimate[lpm$term == 'Opponent: Rank'], digits = 2) == 0)) { # Not significant.
        cat('* The rank of the opponent does not substantially affect the winning probability.\n')
      } else if(!is.na(lpm$estimate[lpm$term == 'Opponent: Rank'])) { # Significant.
        if(lpm$estimate[lpm$term == 'Opponent: Rank'] > 0) {
          cat('* The winning probability increases ')
        } else {
          cat('* Surprisingly, the winning probability decreases ')
        }
        
        cat('with the rank of the opponent.\n')
      }
      
      if(isTRUE(lpm$p.value[lpm$term == 'Opponent: Age'] < 0.1 & round(lpm$estimate[lpm$term == 'Opponent: Age'], digits = 2) != 0)) { # Significant.
        cat('* The winning probability ')
        
        if(lpm$estimate[lpm$term == 'Opponent: Age'] > 0) {
          cat('increases ')
        } else {
          cat('decreases ')
        }
        
        cat('with the age of the opponent.\n')
      }
      
      if(isTRUE(lpm$p.value[lpm$term == 'Opponent: Height'] < 0.1 & round(lpm$estimate[lpm$term == 'Opponent: Height'], digits = 2) != 0)) { # Significant.
        cat('* The winning probability ')
        
        if(lpm$estimate[lpm$term == 'Opponent: Height'] > 0) {
          cat('increases ')
        } else {
          cat('decreases ')
        }
        
        cat('with the height of the opponent.\n')
      }
      
      if(isTRUE(lpm$p.value[lpm$term == 'Opponent: Lefty'] < 0.1 & round(lpm$estimate[lpm$term == 'Opponent: Lefty'], digits = 2) != 0)) { # Significant.
        cat('* The winning probability is ')
        
        if(lpm$estimate[lpm$term == 'Opponent: Lefty'] > 0) {
          cat('larger ')
        } else {
          cat('smaller ')
        }
        
        cat('against lefties.\n')
      }
      
      if(isTRUE(lpm$p.value[lpm$term == 'Opponent: One Handed Backhand'] < 0.1 & round(lpm$estimate[lpm$term == 'Opponent: One Handed Backhand'], digits = 2) != 0)) { # Significant.
        cat('* The winning probability is larger against players with a ')
        
        if(lpm$estimate[lpm$term == 'Opponent: One Handed Backhand'] > 0) {
          cat('one-handed ')
        } else {
          cat('two-handed ')
        } 
        
        cat('backhand.\n')
      }
      
      if(isTRUE(lpm$p.value[lpm$term == 'Best of Five'] < 0.1 & round(lpm$estimate[lpm$term == 'Best of Five'], digits = 2) != 0)) { # Significant.
        cat('* The winning probability is larger in ')
        
        if(lpm$estimate[lpm$term == 'Best of Five'] > 0) {
          cat('best-of-five ')
        } else {
          cat('best-of-three ')
        }
        
        cat('matches.\n')
      }
    }
    
    cat('\nIt should be noted that the R-squared is', rSquared)
    
    if(rSquared < 0.1) {
      cat(', which is very low.') # If the R squared is very low, point it out.
    } else {
      cat('.')
    }
  }
}
```

\vspace{1cm}

# Wins With Fewer Games Than the Opponent
```{r, echo = FALSE, results = 'asis'}
# Objects from report.R:
# - numberOfUnfairWins
# - overview
# - playerName
# - unfairWins

if(overview$active == 0) { # If not active any more, use past simple.
  if(numberOfUnfairWins > 0) { # Check whether the player won any match with fewer games than the opponent.
    cat(playerName, 'won', numberOfUnfairWins, 'matches with fewer games than the opponent. You can see them in the following table:\n')
    
    kable(unfairWins)
  } else {
    cat(playerName, 'did not win any match with fewer games than the opponent.')
  }
} else if(overview$active == 1) { # If still active, use present perfect.
  if(numberOfUnfairWins > 0) { # Check whether the player has won any match with fewer games than the opponent.
    cat(playerName, 'has won', numberOfUnfairWins, 'matches with fewer games than the opponent so far. You can see them in the following table:\n')
    
    kable(unfairWins)
  } else {
    cat(playerName, 'has not won any match with fewer games than the opponent yet.')
  }
}
```
