---
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r, include = FALSE, warning = FALSE}
setwd('../')
source('code/report.R')
source('data/playersCleaned')
```

---
title: 'A Detailed Analysis of `r playerName`'s Results'
author: 'Noah Baiguini, Dorian Böhler'
date: '5/26/2023'
---


**General information about the player **

Here some ground information about `r playerName`
```{r comparisons, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
require(gridExtra)
grid.arrange(informationPlayer ,  ncol=1)
```


<br>

**How much money has the player earned**

`r playerName`  has earned `r totalMoneyEarned` Dollars throughout his whole career. 

<br>

**at which age the player earned the most **

```{r comparisons, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
require(gridExtra)
grid.arrange(ggplot1,  ncol=1)
```
`r playerName` has earned the most at age `r maxAge` with earnings of $ `r maxEarnings`

<br>

**in which country has the player played the most**

The country in which `r playerName` has played the most is `r MostCountryPlayedIn`.


<br>

**win percentage on outdoor and indoor**

`r playerName` has a win percentage of `r percentage1` % on outdoor and a win percentage of `r percentage2` % on indoor fields. 


<br>

**the win percentage in each set**

```{r comparisons, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
require(gridExtra)
grid.arrange(barSet1, barSet2, barSet3, barSet4, barSet5,  ncol=5)

```

`r playerName` has a win percentage in the first set of `r set1WinPercentage` %, in the second one set it is `r set2WinPercentage` %, in the third one it is `r set3WinPercentage` %, in the fourth one `r set4WinPercentage` %, and in the fifth one `r set5WinPercentage` %.

<br>

**the highest World position achieved by the player and for how long he was there**

`r playerName` has his highest world ranking at `r lowestRank`. His has had this position for `r lowestRankCount` weeks. the maximum number of consecuitive weeks he was on that ranking is `r maxConsecuitiveCount`

<br>
