---
output: pdf_document
---

---
author: "Noah Baiguini, Dorian Böhler"
title: "A Detailed Analysis of `r playerName`'s Results"
date: "`r format(Sys.time(), '%d.%m.%Y')`"
---

```{r, echo = FALSE, results = 'asis'}
cat('This report is about **', playerName, '**, who is a tennis player from ', countrycode(overview$country, origin = 'ioc', destination = 'country.name'), '. He turned pro in ', overview$turnedPro, ' and is ', sep = '')
if(overview$active == 1) {
  cat('still active')
} else {
  cat('not active any more')
}
cat('. He was born on ', format(overview$birthday, '%d %B %Y'), ', so he is now ', floor(time_length(Sys.Date() - overview$birthday, 'years')), ' years old.\n', sep = '')

cat('\n', playerName, ' is a ', sep = '')
if(overview$lefty == 1) {
  cat('lefty')
} else {
  cat('righty')
}
cat(' and has a ')
if(overview$oneHandedBackhand == 1) {
  cat('one-handed')
} else {
  cat('two-handed')
}
cat(' backhand.\n')

cat('\nHe ')

if(overview$active == 0) {
  cat('played', numberOfMatches, 'matches in total.')
} else if(overview$active == 1) {
  cat('has played', numberOfMatches, 'matches so far.')
}

cat(' The highest ranking achieved is ', highestRank, '.', sep = '')
```

# Winning percentages
Here are a few interesting match winning percentages:

* Total: `r winningPercentage`
* Outdoor: `r winningPercentageOutdoor`
* Indoor: `r winningPercentageIndoor`
* Hard court: `r winningPercentageHard`
* Clay court: `r winningPercentageClay`
* Grass court: `r winningPercentageGrass`
* Best of three: `r winningPercentageBestOfThree`
* Best of five: `r winningPercentageBestOfFive`
* Against players with a one-handed backhand: `r winningPercentageOneHandedBackhand`
* Against players with a two-handed backhand: `r winningPercentageTwoHandedBackhand`
* Against top 10 players: `r winningPercentageTop10`

&nbsp;

The following figure shows the number of first, second, third, fourth, and fifth sets played and won including the winning percentages:

&nbsp;

```{r, echo = FALSE, fig.height = 2.5}
plotWinningPercentageSets
```

&nbsp;

In the following figure, you can see the winning percentages (matches, sets, and games) over time:

&nbsp;

```{r, echo = FALSE, message = FALSE, fig.height = 3.5}
plotRatio4
```

&nbsp;

# Tournaments
The tournament(s) with the best match winning percentage is (are): `r winningPercentageTournaments`.

The match winning percentages at Grand Slams are as follows:

```{r, echo = FALSE, results = 'asis'}
kable(winningPercentageGrandSlams, col.names = c('Tournament', 'Match Winning Percentage'))
```

# Price Money
`r playerName`'s total price money is `r priceMoneyUSDollarTotal`. On the next page, you can see how it developed over time.

&nbsp;

```{r, echo = FALSE, fig.height = 3.5}
plotPriceMoneyUSDollarTotalYearly
```

&nbsp;

```{r, echo = FALSE, results = 'asis'}
if(overview$active == 1) {
  cat('It should be noted that', year(Sys.Date()), 'is not over yet.')
}
```

# What affects the winning probability of `r playerName`?
We have estimated the effect of some variables on the winning probability, using a linear probability model. The following table shows the results:

```{r, echo = FALSE, results = 'asis'}
kable(lpm %>% mutate(p.value = pvalue(p.value)), col.names = c('Predictor', 'B', 'SE', 't', 'p'), digits = c(0, 2, 3, 3, 3))
```

The base group is `r levels(results$surface)[1]` for the surface. 

Here are a few interesting observations:

```{r, echo = FALSE, results = 'asis'}
if(overview$active == 0) {
  if(lpm$p.value[lpm$term == 'Tournament at Home'] > 0.1 | round(lpm$estimate[lpm$term == 'Tournament at Home'], digits = 2) == 0) {
    cat('* It did not influence the winning probability whether', playerName, 'played at home or not.\n')
  } else {
    cat('*', playerName, 'played ')
    
    if(lpm$estimate[lpm$term == 'Tournament at Home'] > 0) {
      cat('better ')
    } else {
      cat('worse ')
    }
    
    cat('at home.\n')
  }
  
  if(lpm$p.value[lpm$term == 'Outdoor'] < 0.1 & round(lpm$estimate[lpm$term == 'Outdoor'], digits = 2) != 0) {
    cat('*', playerName, 'played better ')
    
    if(lpm$estimate[lpm$term == 'Outdoor'] > 0) {
      cat('outdoor.\n')
    } else {
      cat('indoor.\n')
    }
  }
  
  cat('* It seems that the order of preference for the surface was: ')
  
  if(lpm$estimate[lpm$term == 'Surface: Clay'] < 0 &
     lpm$estimate[lpm$term == 'Surface: Grass'] < lpm$estimate[lpm$term == 'Surface: Clay']) {
    cat('Hard, Clay, and Grass (ignoring Carpet).\n')
  } else if(lpm$estimate[lpm$term == 'Surface: Grass'] < 0 &
            lpm$estimate[lpm$term == 'Surface: Clay'] < lpm$estimate[lpm$term == 'Surface: Grass']) {
    cat('Hard, Grass, and Clay (ignoring Carpet).\n')
  } else if(lpm$estimate[lpm$term == 'Surface: Grass'] > 0 &
            lpm$estimate[lpm$term == 'Surface: Clay'] < 0) {
    cat('Grass, Hard, and Clay (ignoring Carpet).\n')
  } else if(lpm$estimate[lpm$term == 'Surface: Clay'] > 0 &
            lpm$estimate[lpm$term == 'Surface: Grass'] < 0) {
    cat('Clay, Hard, and Grass (ignoring Carpet).\n')
  } else if(lpm$estimate[lpm$term == 'Surface: Clay'] > 0 &
            lpm$estimate[lpm$term == 'Surface: Grass'] > lpm$estimate[lpm$term == 'Surface: Clay']) {
    cat('Grass, Clay, and Hard (ignoring Carpet).\n')
  } else if(lpm$estimate[lpm$term == 'Surface: Grass'] > 0 &
            lpm$estimate[lpm$term == 'Surface: Clay'] > lpm$estimate[lpm$term == 'Surface: Grass']) {
    cat('Clay, Grass, and Hard (ignoring Carpet).\n')
  }
  
  if(lpm$p.value[lpm$term == 'Total Price Money (m$)'] < 0.1 & round(lpm$estimate[lpm$term == 'Total Price Money (m$)'], digits = 2) != 0) {
    cat('*', playerName, 'played ')
    
    if(lpm$estimate[lpm$term == 'Total Price Money (m$)'] > 0) {
      cat('better ')
    } else {
      cat('worse ')
    }
    
    cat('when there was more money to win.\n')
  }
  
  if(lpm$p.value[lpm$term == 'Opponent: Rank'] > 0.1 | round(lpm$estimate[lpm$term == 'Opponent: Rank'], digits = 2) == 0 ) {
    cat('* The rank of the opponent did not substantially affect the winning probability.\n')
  } else {
    if(lpm$estimate[lpm$term == 'Opponent: Rank'] > 0) {
      cat('* The winning probability increased ')
    } else {
      cat('* Surprisingly, the winning probability decreased ')
    }
    
    cat('with the rank of the opponent.\n')
  }
  
  if(lpm$p.value[lpm$term == 'Opponent: Age'] < 0.1 & round(lpm$estimate[lpm$term == 'Opponent: Age'], digits = 2) != 0) {
    cat('* The winning probability ')
    
    if(lpm$estimate[lpm$term == 'Opponent: Age'] > 0) {
      cat('increased ')
    } else {
      cat('decreased ')
    }
    
    cat('with the age of the opponent.\n')
  }
  
  if(lpm$p.value[lpm$term == 'Opponent: Height'] < 0.1 & round(lpm$estimate[lpm$term == 'Opponent: Height'], digits = 2) != 0) {
    cat('* The winning probability ')
    
    if(lpm$estimate[lpm$term == 'Opponent: Height'] > 0) {
      cat('increased ')
    } else {
      cat('decreased ')
    }
    
    cat('with the height of the opponent.\n')
  }
  
  if(lpm$p.value[lpm$term == 'Opponent: Lefty'] < 0.1 & round(lpm$estimate[lpm$term == 'Opponent: Lefty'], digits = 2) != 0) {
    cat('* The winning probability was ')
    
    if(lpm$estimate[lpm$term == 'Opponent: Lefty'] > 0) {
      cat('larger ')
    } else {
      cat('smaller ')
    }
    
    cat('against lefties.\n')
  }
  
  if(lpm$p.value[lpm$term == 'Opponent: One Handed Backhand'] < 0.1 & round(lpm$estimate[lpm$term == 'Opponent: One Handed Backhand'], digits = 2) != 0) {
    cat('* The winning probability was larger against players with a ')
    
    if(lpm$estimate[lpm$term == 'Opponent: One Handed Backhand'] > 0) {
      cat('one-handed ')
    } else {
      cat('two-handed ')
    } 
    
    cat('backhand.\n')
  }
  
  if(lpm$p.value[lpm$term == 'Best of Five'] < 0.1 & round(lpm$estimate[lpm$term == 'Best of Five'], digits = 2) != 0) {
    cat('* The winning probability was larger in ')
    
    if(lpm$estimate[lpm$term == 'Best of Five'] > 0) {
      cat('best-of-five ')
    } else {
      cat('best-of-three ')
    }
    
    cat('matches.\n')
  }
} else if(overview$active == 1) {
  if(lpm$p.value[lpm$term == 'Tournament at Home'] > 0.1 | round(lpm$estimate[lpm$term == 'Tournament at Home'], digits = 2) == 0) {
    cat('* It does not influence the winning probability whether', playerName, 'plays at home or not.\n')
  } else {
    cat('*', playerName, 'plays ')
    
    if(lpm$estimate[lpm$term == 'Tournament at Home'] > 0) {
      cat('better ')
    } else {
      cat('worse ')
    }
    
    cat('at home.\n')
  }
  
  if(lpm$p.value[lpm$term == 'Outdoor'] < 0.1 & round(lpm$estimate[lpm$term == 'Outdoor'], digits = 2) != 0) {
    cat('*', playerName, 'plays better ')
    
    if(lpm$estimate[lpm$term == 'Outdoor'] > 0) {
      cat('outdoor.\n')
    } else {
      cat('indoor.\n')
    }
  }
  
  cat('* It seems that the order of preference for the surface is: ')
  
  if(lpm$estimate[lpm$term == 'Surface: Clay'] < 0 &
     lpm$estimate[lpm$term == 'Surface: Grass'] < lpm$estimate[lpm$term == 'Surface: Clay']) {
    cat('Hard, Clay, and Grass (ignoring Carpet).\n')
  } else if(lpm$estimate[lpm$term == 'Surface: Grass'] < 0 &
            lpm$estimate[lpm$term == 'Surface: Clay'] < lpm$estimate[lpm$term == 'Surface: Grass']) {
    cat('Hard, Grass, and Clay (ignoring Carpet).\n')
  } else if(lpm$estimate[lpm$term == 'Surface: Grass'] > 0 &
            lpm$estimate[lpm$term == 'Surface: Clay'] < 0) {
    cat('Grass, Hard, and Clay (ignoring Carpet).\n')
  } else if(lpm$estimate[lpm$term == 'Surface: Clay'] > 0 &
            lpm$estimate[lpm$term == 'Surface: Grass'] < 0) {
    cat('Clay, Hard, and Grass (ignoring Carpet).\n')
  } else if(lpm$estimate[lpm$term == 'Surface: Clay'] > 0 &
            lpm$estimate[lpm$term == 'Surface: Grass'] > lpm$estimate[lpm$term == 'Surface: Clay']) {
    cat('Grass, Clay, and Hard (ignoring Carpet).\n')
  } else if(lpm$estimate[lpm$term == 'Surface: Grass'] > 0 &
            lpm$estimate[lpm$term == 'Surface: Clay'] > lpm$estimate[lpm$term == 'Surface: Grass']) {
    cat('Clay, Grass, and Hard (ignoring Carpet).\n')
  }
  
  if(lpm$p.value[lpm$term == 'Total Price Money (m$)'] < 0.1 & round(lpm$estimate[lpm$term == 'Total Price Money (m$)'], digits = 2) != 0) {
    cat('*', playerName, 'plays ')
    
    if(lpm$estimate[lpm$term == 'Total Price Money (m$)'] > 0) {
      cat('better ')
    } else {
      cat('worse ')
    }
    
    cat('when there is more money to win.\n')
  }
  
  if(lpm$p.value[lpm$term == 'Opponent: Rank'] > 0.1 | round(lpm$estimate[lpm$term == 'Opponent: Rank'], digits = 2) == 0 ) {
    cat('* The rank of the opponent does not substantially affect the winning probability.\n')
  } else {
    if(lpm$estimate[lpm$term == 'Opponent: Rank'] > 0) {
      cat('* The winning probability increases ')
    } else {
      cat('* Surprisingly, the winning probability decreases ')
    }
    
    cat('with the rank of the opponent.\n')
  }
  
  if(lpm$p.value[lpm$term == 'Opponent: Age'] < 0.1 & round(lpm$estimate[lpm$term == 'Opponent: Age'], digits = 2) != 0) {
    cat('* The winning probability ')
    
    if(lpm$estimate[lpm$term == 'Opponent: Age'] > 0) {
      cat('increases ')
    } else {
      cat('decreases ')
    }
    
    cat('with the age of the opponent.\n')
  }
  
  if(lpm$p.value[lpm$term == 'Opponent: Height'] < 0.1 & round(lpm$estimate[lpm$term == 'Opponent: Height'], digits = 2) != 0) {
    cat('* The winning probability ')
    
    if(lpm$estimate[lpm$term == 'Opponent: Height'] > 0) {
      cat('increases ')
    } else {
      cat('decreases ')
    }
    
    cat('with the height of the opponent.\n')
  }
  
  if(lpm$p.value[lpm$term == 'Opponent: Lefty'] < 0.1 & round(lpm$estimate[lpm$term == 'Opponent: Lefty'], digits = 2) != 0) {
    cat('* The winning probability is ')
    
    if(lpm$estimate[lpm$term == 'Opponent: Lefty'] > 0) {
      cat('larger ')
    } else {
      cat('smaller ')
    }
    
    cat('against lefties.\n')
  }
  
  if(lpm$p.value[lpm$term == 'Opponent: One Handed Backhand'] < 0.1 & round(lpm$estimate[lpm$term == 'Opponent: One Handed Backhand'], digits = 2) != 0) {
    cat('* The winning probability is larger against players with a ')
    
    if(lpm$estimate[lpm$term == 'Opponent: One Handed Backhand'] > 0) {
      cat('one-handed ')
    } else {
      cat('two-handed ')
    } 
    
    cat('backhand.\n')
  }
  
  if(lpm$p.value[lpm$term == 'Best of Five'] < 0.1 & round(lpm$estimate[lpm$term == 'Best of Five'], digits = 2) != 0) {
    cat('* The winning probability is larger in ')
    
    if(lpm$estimate[lpm$term == 'Best of Five'] > 0) {
      cat('best-of-five ')
    } else {
      cat('best-of-three ')
    }
    
    cat('matches.\n')
  }
}

cat('\nIt should be noted that the R-squared is', rSquared)

if(rSquared < 0.1) {
  cat(', which is very low.')
} else {
  cat('.')
}
```

# Wins With Fewer Games Than the Opponent
```{r, echo = FALSE, results = 'asis'}
if(overview$active == 0) {
  if(numberOfUnfairWins > 0) {
    cat(playerName, 'won', numberOfUnfairWins, 'matches with fewer games than the opponent. You can see them in the following table:\n')
    
    kable(unfairWins)
  } else {
    cat(playerName, 'did not win any match with fewer games than the opponent.')
  }
} else if(overview$active == 1) {
  if(numberOfUnfairWins > 0) {
    cat(playerName, 'has won', numberOfUnfairWins, 'matches with fewer games than the opponent so far. You can see them in the following table:\n')
    
    kable(unfairWins)
  } else {
    cat(playerName, 'has not won any match with fewer games than the opponent yet.')
  }
}
```
