---
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r, include = FALSE, warning = FALSE}
setwd('../')
source('code/report.R')
```

---
title: 'A Detailed Analysis of `r playerName`'s Results'
author: 'Noah Baiguini, Dorian Böhler'
date: '5/26/2023'
---


**How much money has the player earned**

```{r comparisons, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
print(paste0(playerName, ' has earned ', totalMoneyEarned, ' Dollars throughout his whole career.'))
```



**...**

```{r comparisons, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Here: compute your code
```

Here: write your comment

<br>

**in which country has the player played the most**

```{r comparisons, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
newTable2 <- results[, c("tournamentStart", "tournamentCountry")]
newTable2 <- unique(newTable2)
countryMostPlayed <- results %>%
  count(tournamentCountry) %>%
  top_n(1, n)

print(paste0('The country in which ', playerName, ' has played the most is:', countryMostPlayed$tournamentCountry))
```

Here: write your comment

<br>

**win percentage on outdoor and indoor**

```{r comparisons, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
newTable3 <- results[, c("tournamentStart", "win", "outdoor")]
newTable3 <- na.omit(newTable3)

#outdoor
percentage1 <- newTable3 %>% 
  filter(outdoor == 1) %>% 
  summarise(percentage = mean(win == 1)) %>% 
  pull(percentage)
#indoor 
percentage2 <- newTable3 %>% 
  filter(outdoor == 0) %>% 
  summarise(percentage = mean(win == 1)) %>% 
  pull(percentage)

print(paste0(playerName, ' has a win percentage of ', round(percentage1, 4), ' on outdoor fields and a win percentage of ', round(percentage2, 4), ' on indoor fields'))

```

Here: write your comment


<br>

**the highest World position achived by the player and for how long he was there**

```{r comparisons, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Print the results
cat(paste0("The highest World ranking achived by ", playerName, " is ", lowestRank, "\n"))
cat(paste0("He was at this world ranking in numbers of weeks : ", lowestRankCount, "\n"))
cat(paste0("The maximum number of consecutive weeks he was on that ranking: ", maxConsecutiveCount, "\n"))

```

Here: write your comment

<br>

**...**

```{r comparisons, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Here: compute your code
```

Here: write your comment

<br>

**...**

```{r comparisons, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Here: compute your code
```

Here: write your comment